
Sentiment Analysis with R



```{r}
install.packages("twitteR")
install.packages("ROAuth")
install.packages("httr")
install.packages("plyr")
install.packages("ggplot2")
install.packages("plotly")
library(twitteR)
library(ROAuth)
library(httr)
library(plyr)
library(ggplot2)
library(plotly)

#Set up API keys and access tokens
api_key <- "QjL56aMf79NSDYnHXFUGjRSuI"
api_secret <- "GvRewQQ5BYv97NIskXuCyIUitQneK1cEXz2ER4L9rN9ky5Ds1l"
access_token <- "711069376779313152-Jy3keltbhnmYy0y71MX0X6Fs0P4pyQf"
access_token_secret <- "LXsPZU2CPvupivnoYe3atVYFPDfsU0LozjHzqkBPGYL32"
setup_twitter_oauth(api_key, api_secret, access_token, access_token_secret)

```
```{r}
#Grab latest tweets

tweets_trump <- searchTwitter('@realDonaldTrump',n = 1500)


feed_trump = laply(tweets_trump, function(t)t$getText())


#Read in dictionary of positive and #negative works
pos = scan('positive-words.txt',what = 'character', comment.char = ';')
neg = scan ('negative-words.txt',what = 'character',comment.char = ';')


score.sentiment = function(sentences, good_text, bad_text, .progress='none')
{
    require(plyr)
    require(stringr)
  
    scores = laply(sentences, function(sentence, good_text, bad_text) {
        
  
        sentence = gsub('[[:punct:]]', '', sentence)
        sentence = gsub('[[:cntrl:]]', '', sentence)
        sentence = gsub('\\d+', '', sentence)
        sentence <- iconv(sentence, 'UTF-8', 'ASCII')
        sentence = tolower(sentence)        
        word.list = str_split(sentence, '\\s+')
        words = unlist(word.list)
        
        # compare our words to the dictionaries of positive & negative terms
        pos.matches = match(words, good_text)
        neg.matches = match(words, bad_text)
        
        # match() returns the position of the matched term or NA
        # Gives only True/False
        pos.matches = !is.na(pos.matches)
        neg.matches = !is.na(neg.matches)
        
        score = sum(pos.matches) - sum(neg.matches)
        
        return(score)
    }, good_text, bad_text, .progress=.progress )
    
    scores.df = data.frame(score=scores, text=sentences)
    return(scores.df)
}

bad_text = c(pos, 'wtf', 'epicfail', 'douchebag')
good_text = c(neg, 'upgrade', ':)', '#iVoted', 'voted')


trump <- score.sentiment(feed_trump, good_text, bad_text, .progress='text')
trump$name <- 'Trump'
# Cut the text, just gets in the way
plotdat <- trump[c("name", "score")]
# Remove neutral values of 0
plotdat <- plotdat[!plotdat$score == 0, ]

#little quick plot
qplot(factor(score), data=plotdat, geom="bar", 
      fill=factor(name),
      xlab = "Sentiment Score")


